Graphical Tests for Power Comparison of Competing Designs

### 2012-03-29 setup.tex
color in plots

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
%\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrrrl}
  \hline
& & Estimate & Error & $z$-value & $p$-value &\\ 
  \hline
\bf design & euclid & -0.08 & 0.39 & -0.21 & 0.84 &\\ 
&polar & -1.98 & 0.32 & -6.13 & 0.00 & ***\\ [3pt]
\multicolumn{2}{l}{\bf main effects} &&&&&\\
& reference line  & -0.14 & 0.26 & -0.53 & 0.59 & \\ [1pt]
&  sample size & 0.27 & 0.04 & 6.31 & 0.00 & ***\\[1pt]
 &offset:  90 degrees& -0.43 & 0.37 & -1.18 & 0.24 &\\ 
  & 180 degrees& -0.89 & 0.35 & -2.51 & 0.01 & **\\ 
  & 270 degrees& 0.21 & 0.38 & 0.55 & 0.58 &\\ [3pt]
\multicolumn{2}{l}{\bf interactions} &&&&&\\
&  polar:line & 0.51 & 0.35 & 1.44 & 0.15 &\\ [1pt]
&    polar:sample size & -0.23 & 0.05 & -5.02 & 0.00 & ***\\[1pt]
&    polar:offset 90 & 0.64 & 0.49 & 1.30 & 0.20 \\ 
&  polar:offset 180 & 0.91 & 0.47 & 1.92 & 0.05 & .\\ 
&    polar:offset 270 & -0.73 & 0.54 & -1.35 & 0.18 &\\
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}
}
\end{center}
\caption{\label{tbl:correct} Output of a generalized linear mixed effects model for power of lineups (i.e. probability of identifying the data plot) for comparing designs. Included are two-way interactions with sample size and shifts in wind direction (offset). Euclidean designs without a reference line at offset 0 are used as 
 Results are based on  976 lineup evaluations by 115 participants. }
\end{table}

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
%\rowcolors{2}{white}{lightgray}
\begin{tabular}{lrrrrrl}
  \hline
& & Estimate & Error & $t$-value & \multicolumn{2}{l}{approx $p$-value} \\ 
  \hline
\bf design & Intercept & 3.58 & 0.09 & 41.34 & 0.00 & ***\\ 
&  polar & 0.22 & 0.10 & 2.17 & 0.03 & * \\ [2pt]
\multicolumn{2}{l}{\bf covariates}\\
&reference line & 0.08 & 0.06 & 1.50 & 0.13 \\ [1pt]
 & sample size & -0.03 & 0.00 & -8.73 & 0.00 & ***\\ [1pt]
&  offset: 90 & -0.06 & 0.08 & -0.72 & 0.47 \\ 
& 180 & 0.16 & 0.08 & 2.07 & 0.04 & *\\ 
&  270 & -0.04 & 0.07 & -0.54 & 0.59 \\ [2pt]
\multicolumn{2}{l}{\bf interactions}\\
&  polar:line & -0.03 & 0.08 & -0.40 & 0.69 \\ [1pt]
&    polar:sample size & 0.03 & 0.01 & 6.25 & 0.00 & ***\\ [1pt]
&    polar:offset 90 & 0.14 & 0.11 & 1.23 & 0.22 \\ 
&    polar:offset 180 & -0.17 & 0.11 & -1.55 & 0.12 \\ 
&    polar:offset 270 & 0.17 & 0.11 & 1.50 & 0.13 \\ 
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}}
\end{center}
\caption{\label{tbl:time} Model output for linear mixed effects model of (log) time taken, barchart design is baseline. }
\end{table}

>>>>

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
%\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrrrl}
  \hline
& & Estimate & Error & $z$-value & $p$-value &\\ 
  \hline
\bf design & euclid & -0.08 & 0.39 & -0.21 & 0.84 &\\ 
&polar & -1.98 & 0.32 & -6.13 & 0.00 & ***\\ [3pt]
\multicolumn{2}{l}{\bf main effects} &&&&&\\
& reference line  & -0.14 & 0.26 & -0.53 & 0.59 & \\ [1pt]
&  sample size & 0.27 & 0.04 & 6.31 & 0.00 & ***\\[1pt]
 &offset:  90 degrees& -0.43 & 0.37 & -1.18 & 0.24 &\\ 
  & 180 degrees& -0.89 & 0.35 & -2.51 & 0.01 & **\\ 
  & 270 degrees& 0.21 & 0.38 & 0.55 & 0.58 &\\ [3pt]
\multicolumn{2}{l}{\bf interactions} &&&&&\\
&  polar:line & 0.51 & 0.35 & 1.44 & 0.15 &\\ [1pt]
&    polar:sample size & -0.23 & 0.05 & -5.02 & 0.00 & ***\\[1pt]
&    polar:offset 90 & 0.64 & 0.49 & 1.30 & 0.20 \\ 
&  polar:offset 180 & 0.91 & 0.47 & 1.92 & 0.05 & .\\ 
&    polar:offset 270 & -0.73 & 0.54 & -1.35 & 0.18 &\\
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}
}
\end{center}
\caption{\label{tbl:correct} Output of a generalized linear mixed effects model for power of lineups (i.e. probability of identifying the data plot) for comparing designs. Included are two-way interactions with sample size and shifts in wind direction (offset). Euclidean designs without a reference line at offset 0 are used as baseline. 
 Results are based on  976 lineup evaluations by 115 participants. }
\end{table}

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
%\rowcolors{2}{white}{lightgray}
\begin{tabular}{lrrrrrl}
  \hline
& & Estimate & Error & $t$-value & \multicolumn{2}{l}{approx $p$-value} \\ 
  \hline
\bf design & Intercept & 3.58 & 0.09 & 41.34 & 0.00 & ***\\ 
&  polar & 0.22 & 0.10 & 2.17 & 0.03 & * \\ [2pt]
\multicolumn{2}{l}{\bf covariates}\\
&reference line & 0.08 & 0.06 & 1.50 & 0.13 \\ [1pt]
 & sample size & -0.03 & 0.00 & -8.73 & 0.00 & ***\\ [1pt]
&  offset: 90 & -0.06 & 0.08 & -0.72 & 0.47 \\ 
& 180 & 0.16 & 0.08 & 2.07 & 0.04 & *\\ 
&  270 & -0.04 & 0.07 & -0.54 & 0.59 \\ [2pt]
\multicolumn{2}{l}{\bf interactions}\\
&  polar:line & -0.03 & 0.08 & -0.40 & 0.69 \\ [1pt]
&    polar:sample size & 0.03 & 0.01 & 6.25 & 0.00 & ***\\ [1pt]
&    polar:offset 90 & 0.14 & 0.11 & 1.23 & 0.22 \\ 
&    polar:offset 180 & -0.17 & 0.11 & -1.55 & 0.12 \\ 
&    polar:offset 270 & 0.17 & 0.11 & 1.50 & 0.13 \\ 
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}}
\end{center}
\caption{\label{tbl:time} Model output for linear mixed effects model of (log) time taken, again, Euclidean designs without a reference line at offset 0 serve as the baseline. }
\end{table}
